Evaluate PEER in each cohort and brain region

### 2021-02-18 combined_analysis/eval_resid_in_each.Rmd
add more summary info

@@

METADATA %>% group_by(Ethnicity, Cohort, Region) %>% dplyr::summarise(count = n()) %>%  kable(caption="Ethnicity, Cohort, Region") %>% kable_styling(full_width=FALSE) 
```

>>>>

```{r cache=FALSE}
knitr::knit_exit()
```

@@

METADATA %>% group_by(Ethnicity, Cohort, Region) %>% dplyr::summarise(count = n()) %>%  kable(caption="Ethnicity, Cohort, Region") %>% kable_styling(full_width=FALSE)

METADATA %>% group_by(Cohort, Region) %>% dplyr::summarise(count = n()) %>%  kable(caption="Cohort, Region") %>% kable_styling(full_width=FALSE) 
```

```{r cache=FALSE}
knitr::knit_exit()
```
